---
title: "Model Improvement, v0.1.0-v0.1.2"
author: "Siddarta Jairam"
date: '`r strftime(Sys.time(),"%A, %B %d, %Y")`'
output: 
  word_document:
    reference_docx: AutoReporttemp.docx
---

```{r setup, include=FALSE}
library(knitr)
library(jpeg)
knitr::opts_chunk$set(fig.width=6.5, fig.height=3,fig.pos='center',echo=FALSE,comment='>',dpi=800)
realWd <- 'C:/Users/Siddarta.Jairam/Documents/MothMigrationModel'
load(paste(realWd,"cfg.Rout",sep="/"))
figList <- list()
source(paste(realWd,"docs/rmdFunctions.R",sep='/'))
findDiff <- function(vecvars,compareInd=1:length(vecvars)){
	first <- compareInd[1]
	cond <- strsplit(vecvars,';')
	diff <- matrix('Same values', nrow = 1, ncol = length(vecvars))
	colnames(diff) <- rwyear
	locCnt <- 1 
	for (var in seq(1,length(cond[[1]]))){
		allCond <- vapply(1:length(vecvars),function(x){
			if(is.element(x,compareInd)){
				cond[[x]][var]
			} else "blank"},'one')
		test <- allCond[compareInd] %in% cond[[first]][var]
		
			
		if(!min(test)){
			#There is a difference between the runs so output it
			if(grepl("=",allCond[[first]])){
				parse <- strsplit(allCond,' = ')
				diff <- rbind(diff,vapply(1:length(vecvars),function(x){
					if(is.element(x,compareInd)){
						parse[[x]][2]
					} else "blank"},'one'))
				nrname <- parse[[first]][1]
			} else {
				diff <- rbind(diff,allCond)
				nrname <- paste0("Starting Location",locCnt)
				locCnt <- locCnt+1
			}
			
			#add the rowname from the thing that is different
			
			rownames(diff)[dim(diff)[1]] <- nrname
			
			#diff <- paste0(diff,paste(allCond,collapse=' != '),'\n')
		}
	}
	
	if (dim(diff)[1]>1){ 
		diff <- diff[-1,,drop=FALSE]
	}
	return(diff)
}
```

This report will compare these runs:

```{r context}
SimDir <- 'C:/Users/Siddarta.Jairam/Documents/Hysplit Out Moth table'
#runs <- c('runDataRedo','runHelloWorld','runInterYear','runFLwinter')
#years <- c('2011','2012','2013','2014')
runs <- c('runInterYear','runAbsFlightLimit','runNightDurDel','runFlightAndNight')
years <- c('2013','2013','2013','2013')
rwyear <- paste(years,runs,sep='/')
fullDir <- paste(SimDir,rwyear,sep='/')
numRuns <- length(rwyear)
compareRuns <- 2:4
cat(paste(rwyear,colllapse='|'))
```

The conditions that the run was done in is as follows:

```{r conditions}
condFiles <- vapply(fullDir,function(x){
	readLines(paste(x,'Conditions.txt',sep='/'))
	},rep('one',5))
cat(condFiles[3:4,2])
```

The differences between the different runs are as follows:

```{r}
bioDiff <- findDiff(condFiles[3,],compareRuns)
simDiff <- findDiff(condFiles[4,],compareRuns)

figList <- updateCntList(figList,"bioDiff")
```

####Table `r figList$bioDiff`. All the differences between the biological Assumptions between the different runs
```{r,results = 'asis'}
kable(as.data.frame(bioDiff),align='c')
figList <- updateCntList(figList,"simDiff")
```

####Table `r figList$simDiff`. All the differences between the parameters for the HYSPLIT execution between the different runs
```{r,results = 'asis'}
kable(as.data.frame(simDiff),align='c')
figList <- updateCntList(figList,"jpgTable")
```

Here is the output:

####Table `r figList$jpgTable`. Contour plots of instaneous snapshots of the Moth population in the different runs at specific times throughout the migration time for FAW throughout late spring to fall.
```{r fig.height=(20/length(rwyear)),fig.show='hold'}
#define jpeg table
times <- c('051','053','063','073','091')
dates <- strftime(strptime(paste0(times,'0'),'%m%d'),'%b\n%d')
numTimes <- length(times)

#fill the table with markdown paths to jpegs
conPaths <- paste(fullDir,'jpeg','Contours',sep='/')
contours <- vapply(conPaths,function(pth){
	vapply(times,function(tim){
		potJpegs <- list.files(pth,
			pattern=paste0('Moth_',tim),
			full.names = TRUE)
		return(potJpegs[!grepl('gsr2',potJpegs)][1])
		},'hi')
	},rep('hi',numTimes))

mosaicImage(contours,labelx=rwyear,labely=dates)
```
